Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/relwk.tex

Nail improves upon Hammer in three ways.  First, Nail generates output in
addition to parsing input.  Second, Nail does not require the programmer
to write potentially insecure semantic actions.  Last, Nail's structural
dependencies and stream transforms allow it to work with protocols that
Hammer cannot handle, such as protocols with offset fields, length fields,
checksums, or compressed data.  (Hammer has limited support for length
fields: it can parse arrays immediately preceded by their length.)

Parsifal~\cite{ANSSI:parsifal} is a parser framework that also supports
generating output for Ocaml.  Parsifal structures grammars as an Ocaml
type that holds an internal model and functions for parsing input and
output.  However, their generator can produce parsers and generators
only for simple, fixed-size structures.  The programmer can then use
these when implementing parsers and generators for more complicated
formats, manually handling offsets, checksums, and the like, risking bugs.
Nail handles more complicated constructs without the programmer manually
writing code to support them.

>>>>

Nail improves upon Hammer in three ways. First, Nail  generates output besides recognizing input.
Second, Nail does not require the programmer to write potentially insecure semantic actions. Last,
Nail's structural dependencies and transformations allow it to work with protocols Hammer cannot recognize, such as
protocols with offset fields or length fields, although Hammer has special facilities for  arrays immediately preceded by their length.

Parsifal~\cite{ANSSI:parsifal} is a parser framework that also supports generating output for Ocaml.
Parsifal structures grammars as an Ocaml type that holds an internal model and functions for parsing
input and output.
However, their generator can only produce parsers and generators for simple, fixed-size structures.
The programmer can then use these when implementing parsers and generators for more
complicated formats, manually handling offsets, checksums and the like, risking bugs. Nail can
handle more complicated constructs without the programmer writing code to support them.
